Paper_stuff

### 2023-09-16 Paper_stuff.Rmd
Updated Tx responders varaibles

Pre_Post
```{r}
Mothership_post <- Mothership |>
  #1. Filter out scores for people not in the program / don't have dataa
  filter(!is.na(Days_complete_1)) |>
    #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
  filter(!Days_complete_1 > 40,
         !Days_complete_1 == 0,
         !is.na(BL_CUXOS),
         !is.na(SUManx_DC),
         BL_CUXOS > 1,
         SUManx_DC > 0,
         !is.na(BL_CUDOS),
         !is.na(SUMdep_DC),
         BL_CUDOS > 1,
         SUMdep_DC > 0
         ) |>
  mutate(
    Delta_Anx_DC = BL_CUXOS - SUManx_DC,
    Delta_Dep_DC = BL_CUDOS - SUMdep_DC,
    Percent_anx_change = SUManx_DC - BL_CUXOS/BL_CUXOS,
    Percent_Dep_Dchange = SUMdep_DC - BL_CUDOS/BL_CUDOS,
    #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
    Anx_Responder = as.factor(
      ifelse(BL_CUXOS > 10 &(Delta_Anx_DC/BL_CUXOS) <= .5 & (Delta_Anx_DC/BL_CUXOS) >= 0, "Anx Responder",
      ifelse(BL_CUXOS > 10 & Delta_Anx_DC/BL_CUXOS < 0, "Anx Worse", 
      ifelse(BL_CUXOS > 10 & Delta_Anx_DC/BL_CUXOS < 1 & Delta_Anx_DC/BL_CUXOS > .5,  "Unresponders", "Low BL Anx"      
      )))),
    Dep_Responder = as.factor(
      ifelse(BL_CUDOS > 10 & (Delta_Dep_DC/BL_CUDOS) <= .5 & (Delta_Dep_DC/BL_CUDOS) >= 0, "Dep Responder",
      ifelse(BL_CUDOS > 10 & Delta_Dep_DC/BL_CUDOS < 0, "Dep Worse", 
      ifelse(BL_CUDOS > 10 & Delta_Anx_DC/BL_CUXOS <= 1 & Delta_Anx_DC/BL_CUXOS > .5,  "Unresponders", "Low BL Dep" 
      )))),
    Treatment_Responder = as.factor(
      ifelse(BL_CUXOS > 10 & (Delta_Anx_DC/BL_CUXOS) < .5 & (Delta_Anx_DC/BL_CUXOS) >= 0, "Anx Responder",
      ifelse((Delta_Dep_DC/BL_CUDOS) < .5 & (Delta_Dep_DC/BL_CUDOS) >= 0, "Dep Responder",
      ifelse(BL_CUXOS > 10 & BL_CUDOS > 10 &(Delta_Anx_DC/BL_CUXOS) < .5 & (Delta_Anx_DC/BL_CUXOS) >= 0 & (Delta_Dep_DC/BL_CUDOS) < .5 & (Delta_Dep_DC/BL_CUDOS) >= 0, "Both_Responder", 
      ifelse(BL_CUXOS > 10 & Delta_Anx_DC/BL_CUXOS < 0, "Anx Worse",
      ifelse(BL_CUDOS > 10 & Delta_Dep_DC/BL_CUDOS < 0, "Dep Worse",
      ifelse(BL_CUXOS > 10 & BL_CUDOS > 10 & Delta_Anx_DC/BL_CUXOS < 1 & Delta_Anx_DC/BL_CUXOS >= .5 & Delta_Dep_DC/BL_CUDOS < 1 & Delta_Dep_DC/BL_CUDOS >= .5, "Both Unresponder",
      ifelse(BL_CUDOS > 10 & Delta_Dep_DC/BL_CUDOS < 1 & Delta_Dep_DC/BL_CUDOS >= .5, "Dep Unresponders", 
      ifelse(BL_CUXOS > 10 & Delta_Anx_DC/BL_CUXOS < 1 & Delta_Anx_DC/BL_CUXOS >= .5, "Anx Unresponders", "Low Baseline"
      ))))))))))

@@

ggplot(Mothership_post, aes(x = Treatment_Responder)) +
  geom_bar() +
  coord_flip() +
  labs(
    title = "Treatment response of Anxiety and Depression",
    subtitle = "Response = 50% reduciton in scores if BL score > 10")

@@

mean(Mothership_post$Percent_anx_change)
ggplot(Mothership_post,aes(x = Anx_Responder, y = Percent_anx_change)) +
         geom_boxplot()
#2. Create pre_scores
      # CUXOS_pre = Day1_CUXOS,
      # CUDOS_pre = Day1_CUDOS
      # )

@@

>>>>

Pre_Post
```{r}
Mothership_post <- Mothership |>
  #1. Filter out scores for people not in the program / don't have dataa
  filter(!is.na(Days_complete_1)) |>
    #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
  filter(!Days_complete_1 > 40,
         !Days_complete_1 == 0,
         !is.na(BL_CUXOS),
         !is.na(SUManx_DC),
         BL_CUXOS > 1,
         SUManx_DC > 0,
         !is.na(BL_CUDOS),
         !is.na(SUMdep_DC),
         BL_CUDOS > 1,
         SUMdep_DC > 0
         ) |>
  mutate(
    Delta_Anx_DC =  SUManx_DC - BL_CUXOS,
    Delta_Dep_DC = SUMdep_DC - BL_CUDOS,
    Percent_Anx_change = (Delta_Anx_DC/BL_CUXOS)*100,
    Percent_Dep_Dchange = (Delta_Dep_DC/BL_CUDOS)*100,
    #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
    Anx_Responder = as.factor(
      ifelse(BL_CUXOS > 10 & Percent_Anx_change  <= -50, "Anx Responder",
      ifelse(BL_CUXOS > 10 & Percent_Anx_change > 0, "Anx Worse", 
      ifelse(BL_CUXOS > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50,  "Unresponders", "Low BL Anx"      
      )))),
    Dep_Responder = as.factor(
      ifelse(BL_CUDOS > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
      ifelse(BL_CUDOS > 10 & Percent_Dep_Dchange > 0, "Dep Worse", 
      ifelse(BL_CUDOS > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50,  "Unresponders", "Low BL Dep" 
      )))),
    Treatment_Responder = as.factor(
      ifelse(BL_CUXOS > 10 & BL_CUXOS > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
      ifelse(BL_CUXOS > 10 & Percent_Anx_change  <= -50, "Anx Responder",
      ifelse(BL_CUDOS > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
      ifelse(BL_CUDOS > 10 & Percent_Dep_Dchange > 0 & BL_CUXOS > 10 & Percent_Anx_change > 0, "Both Worse",
      ifelse(BL_CUXOS > 10 & Percent_Anx_change > 0, "Anx Worse",
      ifelse(BL_CUDOS > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
      ifelse(BL_CUXOS > 10 & BL_CUDOS > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
      ifelse(BL_CUDOS > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
      ifelse(BL_CUXOS > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
      )))))))))))

@@

ggplot(Mothership_post, aes(x = Treatment_Responder)) +
  geom_bar() +
  coord_flip() +
  scale_x_discrete(limits =c("Low Baseline", "Both Worse", "Dep Worse", "Anx Worse","Both Unresponder","Dep Unresponders", "Anx Unresponders","Both_Responder", "Anx Responder","Dep Responder"))+
  labs(
    title = "Treatment response of Anxiety and Depression",
    subtitle = "Response = 50% reduciton in scores if BL score > 10")

@@

mean(Mothership_post$Percent_anx_change)
ggplot(Mothership_post,aes(x = Anx_Responder, y = Percent_Anx_change)) +
         geom_boxplot() +
         ylim(-50,500) + 
  scale_x_discrete(limits = c(
    ""
  ))

#2. Create pre_scores
      # CUXOS_pre = Day1_CUXOS,
      # CUDOS_pre = Day1_CUDOS
      # )

@@

(40-50)/50
```
